---
title: "707_Data_Creation"
output: html_document
date: "2022-08-20"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tidyverse)
library(reticulate)
library(stringr)
library(tigris)
library(maps)
library(usmap)
library(tmap)
library(leaflet)
library(readr)

setwd("C:/Users/hadsa/OneDrive/Documents/Repo/Green Space Project/Data/")



```


## Reading Datasets

Please note our CSV File Names may be different.
```{r}
#IHME_USA_COUNTY_CANCER_MORTALITY_RATES_1980_2014_NATIONAL_Y2017M01D24 dataset
br <- readxl::read_xlsx("~/breast_cancer.xlsx", sheet = "Breast cancer")

#SVI 2014
svi14 <-  read.csv("~/SVI2014_US.csv")

#SVI 2010
svi10 <-  read.csv("~/SVI2010_US.csv")

#NaNDA Pollutant Dataset
pol <- read.csv("~/nanda_pollutst_tract_2000-2018_01P.csv")

#NaNDA Greenspace Dataset
gs <- read.csv("~/nanda_gs.csv")
```
Breast Cancer Data Organization

```{r}
#Fixing Names
colnames(br) <- br[1,]

#Deleting Duplicate Name Row and National Row
br <- br[c(-1,-2),]



#Removing State Row
br$FIPS <- as.numeric(br$FIPS)

br <- br %>% filter(
  FIPS > 100
)

#Checking
glimpse(br)

#Filtering for relevant data:
br <- br %>% 
  select(Location, FIPS, `Mortality Rate, 2010*`)

#Removing Confidence Intervals
br$`Mortality Rate, 2010*` <- 
  substr(br$`Mortality Rate, 2010*`, 1, 5)

#Changing name of Mortality Rate
colnames(br) <- c("Location", "FIPS", "mx")

#Changing Data Type of Mortality Rate
br$mx <- as.numeric(br$mx)

#Adding Year Vector
br$year <- rep(2010, nrow(br))
```



## Name Changes

Getting the SVI 2010 colnames to matchup, where appropriate, to the SVI 2014 colnames (for general use sake). Once these are made, we can consolidate the datasets. Note that the Breast Cancer Dataset ("br") needs to be merged with SVI 2010 by county FIPS codes. The SVI 2010 has both county FIPS codes and census tract FIPS codes. Once this merge occurs, the breast cancer mortality can be matched up with the census tract FIPS codes in the NaNDA datasets ("gs" and "pol"). There should be duplicate mortality rates per row since census tracts FIPS codes mark geographic regions nested within County Level FIPS marked areas.

```{r}
my.names <- vector(length = ncol(svi10))


# -----Loops----- 


for (i in 1:length(colnames(svi10))){
 
  my.names[i] <- str_replace_all(colnames(svi10)[i], "E_PL_", "EPL_")
  
  my.names2 <- my.names
}

for (i in 1:length(colnames(svi10))){
 
  my.names2[i] <- str_replace_all(my.names2[i], "S_PL_", "SPL_")
  
  my.names3 <- my.names2
}

for (i in 1:length(colnames(svi10))){
 
  my.names3[i] <- str_replace_all(my.names3[i], "R_PL_", "RPL_")
  
  my.names4 <- my.names3
}

for (i in 1:length(colnames(svi10))){
 
  my.names4[i] <- str_replace_all(my.names4[i], "E_P_", "EP_")
  
  my.names5 <- my.names4
}

for (i in 1:length(colnames(svi10))){
 
  my.names5[i] <- str_replace_all(my.names5[i], "M_P_", "MP_")
  
  my.names6 <- my.names5
}
# -----Remove superfluous values--------
remove(my.names)
remove(my.names2)
remove(my.names3)
remove(my.names4)
remove(my.names5)

length(
  intersect(my.names6, colnames(svi14)
            )
  )

intersect(my.names6, colnames(svi14))

# ----The rest-----

colnames(svi10) <- my.names6

remove(my.names6)
```


## Consolidating 

Stacking svi10 (renamed columns) and svi14.

```{r}
# svi merge and clean work
svi <- bind_rows(svi10, svi14)
```


Left Joining Cancer Data & Environmental/Socioeconomic data by common counties (FIPS code)

```{r}
#svi10 work


colnames(svi10)[6] <- "STCNTY"


#gs work
gs <- gs %>% filter(year_intp == 2010) 

colnames(gs)[1] <- "FIPS"
colnames(gs)[2] <- "year"

#br work
br

colnames(br)[2] <- "STCNTY"

#pol work

pol <- pol %>% filter(year == "2010")

colnames(pol)[1] <- "FIPS"

#merge work

df <- merge(svi10, br, by = "STCNTY")

df <- merge(df, pol, by = "FIPS")

df <- merge(df, gs, by = "FIPS")
```

```{r}
environment(remove(pol))
environment(remove(svi14))
environment(remove(br))
environment(remove(svi10))
environment(remove(svi))
```
