---
title: "Exploratory Data Analysis"
author: "Haddon, Trevor, Scott"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(patchwork)
library(cluster)
library(factoextra)
library(here)
```

```{r}
df <- read_csv(here("Data", "cancer_mortality_SES.csv"))
```

```{r}
# separate NaNDA data
nanda <-
  df[, grep("^(value|prop|count_tri_facilities)", colnames(df))]
```

The data has a clean format with no missing data. 

The number of EPA Toxics Release Inventory sites in tract+0.5 mile buffer has a strong positive skewness. Majority of the observations have zero, so we transform the scale on the y-axis.

```{r}
ggplot(data = nanda, aes(x = count_tri_facilities)) +
  geom_histogram(bins = 10, color = "gray") +
  scale_y_log10() +
  theme_bw() +
  labs(x = "number of EPA Toxics Release Inventory sites")
```


For each type of land cover in a census tract, the dataset provides two measures: the original area (in square meter) and the proportion of the area. Therefore, we want to investigate if there is a systematic pattern between the raw area and the proportion. We plot the density plots for both measures and calculate the correlation between the measures. Based on the results, we observe that there is no linear relationship between the two measures. It is reasonable to use both types of measures as predictors.

```{r}
#' Generate density plots for raw area and proportion
#' 
#' @param var_id int
#' @param nanda dataframe
#' @return patchwork ggplot
#' @examples
density_plot <- function(var_id, nanda, title) {
  val_p <- ggplot(data = nanda) +
    geom_density(aes_string(x = paste("value", var_id, sep = "_")), fill = "gray") +
    labs(x = "Area", title = title)
  prop_p <- ggplot(data = nanda) +
    geom_density(aes_string(x = paste("prop_value", var_id, sep = "_")), fill = "gray") +
    labs(x = "Proportion area")
  val_p + prop_p
}
```

```{r}
# get var_ids
var_ids <-
  grep("\\d$", colnames(nanda), value = TRUE) %>% # screen thru all column names and get those ends with digits
  str_split("_") %>% # split each string elem in vector
  sapply(function(x)
    # get last elem of for each list elem
    x[length(x)]) %>%
  unique() # get the unique id

set.seed(121)
var_ids.sample <- sample(var_ids, 3)
```

```{r, fig.width=8}
p <- density_plot(var_ids.sample[1], nanda)
for (id in var_ids.sample[-1]) {
  p <- p / density_plot(id, nanda)
}
p & theme_bw()
```

```{r}
cors <- c()
for (id in var_ids) {
  cors <- append(cors, cor(nanda[paste("value", id, sep = "_")],
                           nanda[paste("prop_value", id, sep = "_")]))
}
tibble(`area type` = var_ids, `correlation` = round(cors, 3)) %>% 
  t() %>% 
  kableExtra::kbl(booktabs = TRUE, digits = 3, col.names = NULL) %>% 
  kableExtra::kable_styling()
```

```{r}
nanda.pca <- prcomp(nanda, center = TRUE, scale. = TRUE)
```

```{r}
summary(nanda.pca)
```


```{r}
var_explained_df <- data.frame(
  PC = seq_len(35),
  var_explained = (nanda.pca$sdev)^2 / sum((nanda.pca$sdev)^2)
)
var_explained_df %>%
  ggplot(aes(x = PC, y = var_explained, group = 1)) +
  geom_point(size = 4) +
  geom_line() +
  labs(title = "Scree plot: PCA on scaled data", y = "Variance explained")
```

```{r}
dim2_nanda <- nanda.pca$x[,c("PC1", "PC2")]
```

```{r}
k3 <- kmeans(dim2_nanda, centers = 3, nstart = 25)
fviz_cluster(k3, data = dim2_nanda, geom="point")
```


